---
title: "Assignment 1 cnt"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
Bikeshare <- read.csv("Bikeshare.csv")
```

###1. Identify the variable type (quantitative (continuous or discrete), categorical (nominal, binary, or ordinal). Explain your reasoning.

The number of bike rentals (cnt) is a discrete quantitative variable. The number of bike rentals can not take on all numbers on an interval as it is not possible to rent half a bike thus it can not be classified as a continuous variable.

###2. Using R, create an appropriate graphic showing the distribution of the data for the respective variable. Remember labels and titles.

```{r echo = FALSE}
cnt.histogram <- ggplot(Bikeshare, aes(x=cnt)) + geom_histogram(breaks=seq(0,10000, by = 622), color = "darkblue", fill = "lightblue") + labs(title = "Number of Bike rentals" ) + xlab("Number of Bike Rentals") + ylab("Total Days")
cnt.histogram
```

###3.	Discuss the distribution for each variable based on the graphs in #2. 
#### •	For categorical, compare counts or proportions between categories. Do they look as you’d expect, given the definitions of the variables? 
#### •	For quantitative, discuss the approximate center, range, shape, and outliers (if any).

Temperature has a mean `r mean(Bikeshare$cnt)` (median: `r (median(Bikeshare$cnt))`). With a minimum of `r min(Bikeshare$cnt)` and max `r max(Bikeshare$cnt)`. The distribution is roughly normal and from the 1.5 * IQR rule there are no possible outliers.

###4.	Compute appropriate summary statistics for each variable.

```{r echo = FALSE}
writeLines("Summary Statistics for Bike Rentals")
summary(Bikeshare$cnt)
writeLines("Standard Deviation =")
sd(Bikeshare$cnt)
writeLines(" ")
writeLines("Number of Observations")
nrow(Bikeshare)
```