---
title: "Assignment 1 Temperature"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
Bikeshare <- read.csv("Bikeshare.csv")
```

###1. Identify the variable type (quantitative (continuous or discrete), categorical (nominal, binary, or ordinal). Explain your reasoning.

Temperature is a continuous quantitative variable, due to temperature values not being disjointed and being able to take on any value between the interval of 0 to 1.

###2. Using R, create an appropriate graphic showing the distribution of the data for the respective variable. Remember labels and titles.

```{r echo = FALSE}
temp.histogram <- ggplot(Bikeshare, aes(x=temp)) + geom_histogram(breaks=seq(0,1, by = 0.125), color = "darkblue", fill = "lightblue") + labs(title = "Temperature Over 2011-2012") + xlab("Normalized Air Temperature") + ylab("Days")
temp.histogram
```

###3.	Discuss the distribution for each variable based on the graphs in #2. 
#### •	For categorical, compare counts or proportions between categories. Do they look as you’d expect, given the definitions of the variables? 
#### •	For quantitative, discuss the approximate center, range, shape, and outliers (if any).


Temperature has a mean `r mean(Bikeshare$temp)` (median: `r (median(Bikeshare$temp))`). With a minimum of `r min(Bikeshare$temp)` and max `r max(Bikeshare$temp)`. The distribution is roughly bimodal and from the 1.5 * IQR rule there are no possible outliers.

###4.	Compute appropriate summary statistics for each variable.

```{r echo = FALSE}
writeLines("Summary Statistics for Temperature")
summary(Bikeshare$temp)
writeLines("Standard Deviation =")
sd(Bikeshare$temp)
writeLines(" ")
writeLines("Number of Observations")
nrow(Bikeshare)
```