---
title: "Assignment 1 Weather"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
Bikeshare <- read.csv("Bikeshare.csv")
```

###1. Identify the variable type (quantitative (continuous or discrete), categorical (nominal, binary, or ordinal). Explain your reasoning.

Weather is a categorical variable under a nominal scale. Types of weather are disjointed categories and have been assigned arbitary values to distinguish between them.

###2. Using R, create an appropriate graphic showing the distribution of the data for the respective variable. Remember labels and titles.

``` {r echo = FALSE}
Bikeshare$weather <- factor(Bikeshare$weather, levels = c("1","2","3","4"))
weather.barplot <- ggplot(data = Bikeshare) + geom_bar(mapping = aes(x = weather)) + labs(title = "Weather Over 2011-2012") + scale_x_discrete(breaks = c(1, 2, 3, 4), labels = c("Clear/partly cloudy", "Mist/cloudy/partly cloudy", "Light rain/snow", "Heavy rain/snow/storm"), drop = FALSE) + ylab("Days") + xlab("Weather")
plot(weather.barplot)
```

###3.	Discuss the distribution for each variable based on the graphs in #2. 
#### •	For categorical, compare counts or proportions between categories. Do they look as you’d expect, given the definitions of the variables? 
#### •	For quantitative, discuss the approximate center, range, shape, and outliers (if any).

For the categorical variable of weather the proportion between categories was not as expected. It was suprising to see 0 counts of heavy rain/snow/storm across two years. however after examining the data table, there was indeed no count for that type of weather.

###4.	Compute appropriate summary statistics for each variable.

```{r echo = FALSE}
meme <- matrix(c(463,63.34, 247,33.79, 21,2.87, 0,0), nrow = 4, ncol = 2, byrow = TRUE,
               dimnames = list(c("clear/partly cloudy", "mist/cloudy/partly cloudy", "light rain/snow", "heavy rain/snow/storm"),
                               c("Count", "Percentage")))
print(meme)
```