---
title: "Assignment 1A, Year"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
Bikeshare <- read.csv("Bikeshare.csv")
```

###1. Identify the variable type (quantitative (continuous or discrete), categorical (nominal, binary, or ordinal). Explain your reasoning.

Years are a categorical variable under an ordinal scale. In this case the years are disjointed categories, being cateogrized as 2011 or 2012. In addition there is ranked ordering of the years, making it an ordinal variable.

###2. Using R, create an appropriate graphic showing the distribution of the data for the respective variable. Remember labels and titles.

```{r echo = FALSE}
yr.barplot <- ggplot(data = Bikeshare) + geom_bar(mapping = aes(x = yr)) + labs(title = "Days in Each Year") + scale_x_continuous(breaks = c(0, 1), labels = c("2011", "2012"))
plot(yr.barplot)
```

###3.	Discuss the distribution for each variable based on the graphs in #2. 
#### •	For categorical, compare counts or proportions between categories. Do they look as you’d expect, given the definitions of the variables? 
#### •	For quantitative, discuss the approximate center, range, shape, and outliers (if any).

The number of counts is as expected for this categorical variable. Each year should have the same amount of days, with the exception of possible leap years. As seen on the bar plot the two years are nearly equal, and within the summary table it can be observed that 2012 was a leap year.

###4.	Compute appropriate summary statistics for each variable.

``` {r echo = FALSE}
yr.setup <- table(Bikeshare$yr)
yr.table = cbind(yr.setup, round(prop.table(yr.setup)*100,2))
colnames(yr.table) = c("Count", "Percentage")
rownames(yr.table) = c("2011", "2012")
writeLines("Summary Statistics for Years (Days)")
print(yr.table)
```